%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{empheq}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{color}
\usepackage{psfrag}
\usepackage{pgfplots}
\usepackage{bm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Other Settings

%%%%%%%%%%%%%%%%%%%%%%%%%% Page Setting %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\geometry{a4paper}

%%%%%%%%%%%%%%%%%%%%%%%%%% Define some useful colors %%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{ocre}{RGB}{243,102,25}
\definecolor{mygray}{RGB}{243,243,244}
\definecolor{deepGreen}{RGB}{26,111,0}
\definecolor{shallowGreen}{RGB}{235,255,255}
\definecolor{deepBlue}{RGB}{61,124,222}
\definecolor{shallowBlue}{RGB}{235,249,255}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%% Define an orangebox command %%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\orangebox[1]{\fcolorbox{ocre}{mygray}{\hspace{1em}#1\hspace{1em}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% English Environments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheoremstyle{mytheoremstyle}{3pt}{3pt}{\normalfont}{0cm}{\rmfamily\bfseries}{}{1em}{{\color{black}\thmname{#1}~\thmnumber{#2}}\thmnote{\,--\,#3}}
\newtheoremstyle{myproblemstyle}{3pt}{3pt}{\normalfont}{0cm}{\rmfamily\bfseries}{}{1em}{{\color{black}\thmname{#1}~\thmnumber{#2}}\thmnote{\,--\,#3}}
\theoremstyle{mytheoremstyle}
\newmdtheoremenv[linewidth=1pt,backgroundcolor=shallowGreen,linecolor=deepGreen,leftmargin=0pt,innerleftmargin=20pt,innerrightmargin=20pt,]{theorem}{Theorem}[section]
\theoremstyle{mytheoremstyle}
\newmdtheoremenv[linewidth=1pt,backgroundcolor=shallowBlue,linecolor=deepBlue,leftmargin=0pt,innerleftmargin=20pt,innerrightmargin=20pt,]{definition}{Definition}[section]
\theoremstyle{myproblemstyle}
\newmdtheoremenv[linecolor=black,leftmargin=0pt,innerleftmargin=10pt,innerrightmargin=10pt,]{problem}{Problem}[section]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Plotting Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepgfplotslibrary{colorbrewer}
\pgfplotsset{width=8cm,compat=1.9}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title & Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \title{Title}
% \author{Haoyun Qin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    % \maketitle
   \section{Methodology}\label{sec:methodology} % (fold)
   \subsection{Research Design and Approach}
   A \textbf{mixed-methods approach} will be employed to develop and evaluate energy-efficient and sustainable cooling innovations for older vehicles lacking factory-installed air conditioning or those with non-functional systems due to age and extensive use. Design-based research will be utilized, emphasizing iterative design, development, and real-world testing. This approach enables both quantitative evaluation of cooling performance and qualitative assessment of user experience and feasibility.
  % subsection  (end)
\subsection{Baseline Assessment and Data Collection}
This phase establishes an understanding of thermal challenges and user needs in older vehicles through:
	\begin{itemize}
	\item \textbf{Literature Review:} - Existing literature on vehicle cooling solutions will be reviewed, focusing on energy efficiency, sustainability, retrofitting options, and challenges specific to older designs. Academic papers, industry reports, and patent searches will be included.
	\item  \textbf{On-Site Temperature Measurements:} Baseline temperature data will be collected inside a representative sample of older vehicles using calibrated sensors and data loggers. Measurements will be taken under varying ambient conditions (e.g., sunny vs. shaded, different times of day) to assess heat build-up and identify critical cooling areas. Key metrics will include in-cabin, dashboard, and seat temperatures. Data will be analyzed using descriptive statistics to determine average and peak temperatures.
	\item \textbf{Surveys and Interviews:} Owners of older vehicles without air conditioning in the target region will be surveyed or interviewed to assess heat discomfort, current cooling strategies, desired features, and potential adoption barriers (e.g., cost, installation complexity). Responses will be analyzed thematically.
       \end{itemize}
       \subsection{Innovation Development and Prototyping}

Based on the needs assessment, cooling solutions tailored for older vehicles will be developed through:
\begin{itemize}
	\item \textbf{Ideation Workshops:} Brainstorming sessions with researchers and field experts will explore cooling technologies such as evaporative cooling, thermoelectric systems, passive ventilation, improved insulation, and solar-powered solutions. Factors like energy efficiency, retrofit compatibility, and cost-effectiveness will be considered.
	\item  \textbf{Concept Selection and Refinement:} Promising ideas will be evaluated based on cooling potential, energy consumption, sustainability, retrofitting feasibility, cost, and user acceptance. Selected concepts will undergo further development.
	\item   \textbf{Prototyping and Iterative Design:} Functional prototypes will be developed using rapid prototyping techniques (e.g., 3D printing, modular components). Designs will prioritize integration with existing vehicle systems and aesthetics.
\end{itemize}
\subsection{Performance Evaluation and Testing}
Prototypes will undergo rigorous testing under controlled and real-world conditions to assess cooling effectiveness and energy efficiency:
\begin{itemize}
	\item \textbf{Laboratory Testing:} Prototypes will be tested in an environmental chamber simulating various temperatures and solar radiation levels. Key metrics include temperature reduction, cooling capacity, energy consumption, airflow rate, and response time. Standardized procedures will be followed where applicable.
	\item \textbf{On-Vehicle Testing:} Prototypes will be installed in older vehicles and tested under real driving conditions. Performance will be compared against baseline (no cooling system) under similar conditions.
	\item \textbf{Energy Efficiency Assessment:} Energy consumption will be measured and compared to traditional AC systems and alternative cooling methods. A Life Cycle Assessment will evaluate environmental impact, including material sourcing, manufacturing, operation, and disposal.
\end{itemize}

Quantitative data will be analyzed using statistical methods, while qualitative feedback will assess usability and user perceptions.
\subsection{Feasibility and Sustainability Assessment}
The most promising innovations will undergo further evaluation:
\begin{itemize}
	\item \textbf{Cost Analysis:} Manufacturing, installation, and potential market pricing will be estimated, prioritizing affordability for owners of older vehicles.
	\item \textbf{Sustainability Assessment: }Environmental impact will be evaluated, including material recyclability, disposal, and long-term energy savings.
	\item \textbf{User Feedback and Refinement:} Additional feedback will be gathered through focus groups or surveys to assess acceptance and identify remaining adoption barriers, informing final refinements.
\end{itemize}

\subsection{Data Analysis}
Quantitative data will be analyzed using descriptive and inferential statistics to compare performance metrics. Qualitative data (surveys, interviews, user feedback) will undergo thematic analysis to identify recurring patterns and insights guiding design improvements.

\subsection{Limitation}
Potential limitations include:
\begin{itemize}
\item Focus on technical performance rather than extensive market analysis.
\item Prototype development constraints due to budget and timeframe.
\item Generalizability to all climates may require further investigation.
\end{itemize}

% section Methodology (end) 

\end{document}
